---
title: "p8105_hw5_zx2424"
author: "Zhaoqianyu Xiong"
date: "2022-11-16"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1
Iterate over file names and read in data for each subject and save the results as a new variable full_df.
```{r}
full_df = 
  tibble(
    files = list.files("./data/"),
    path = str_c("./data/", files) ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest(cols = c(data))
```

Tidy the results.
```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>%  
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome) 

tidy_df
```

Make a spaghetti plot showing observations on each subject over time. For the control group, their outcomes do not change over time, while the outcomes for experiment group increase over time.
```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

## Problem 2
Import the data and create a city_state variable.
```{r}
homicide = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>%
  janitor::clean_names() %>%
  mutate(city_state = str_c(city, sep = ",", state)) %>%
  mutate(status = ifelse(disposition == "Closed by arrest", "0", "1")) %>%
  mutate(status = as.integer(status)) 
```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
homicide_nest = 
  homicide %>%
  select(city_state, status) %>%
  nest(data = status)

total_and_unsolved = 
  function(df){
    total_df = as.integer(count(df))
    unsolved_df = sum(df)
    
    tibble(total = total_df,
         unsolved = unsolved_df)
  }

n_total_unsolved = 
  homicide_nest %>%
  mutate(model1 = map(homicide_nest$data, total_and_unsolved)) %>%
  unnest(model1) %>%
  select(-data)

n_total_unsolved
```

Estimate the proportion of unsolved homicides for Baltimore, MD.
```{r}
output_Baltimore = 
prop.test(x = n_total_unsolved$unsolved[3], n = n_total_unsolved$total[3]) %>%
  broom::tidy() %>%
  select(estimate, starts_with("conf"))

output_Baltimore 
```

Write a function that can generate the results -- estimated proportion and confidence interval.
```{r}
p_and_CI =
  function(x, n) {
     prop.test(x, n) %>%
      broom::tidy() %>%
      select(estimate, starts_with("conf"))
  }
```
